Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-04-06 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
Initial commit

---
title: "Tropical Andes montane and lowland forest plant species GBIF"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "TropAndes_GBIF_plant_occ.csv"
project: "Frugivoria"
date: "2023-04-06"
output: html_document
---

@@

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?permalink=9621ab77-2341-4bf8-9557-b7f19f7f2a35
```{r}
plants_habitats <- read.csv(file.path(data_path,"IUCN/Tropical Andes Plants - Search Results/habitats.csv"))
```

# Create species list from IUCN data
```{r}
plant_species <- unique(plants_habitats$scientificName)
```

# Match species names to GBIF
```{r}
gbif_taxon_keys <- plant_species %>% 
name_backbone_checklist() %>% # match to backbone 
filter(!matchType == "NONE") %>% # get matched names
pull(usageKey) 
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_plant_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
```

>>>>

---
title: "Tropical Andes montane and lowland forest bird and mammal species GBIF"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "TropAndes_GBIF_frugivore_occ.csv"
project: "Frugivoria"
date: "2023-04-06"
output: html_document
---

@@

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?permalink=f4407d96-c039-413a-8d46-707f262271ee
```{r}
frugivore_habitats <- read.csv(file.path(data_path,"IUCN/Tropical Andes Birds and Mammals - Search Results/habitats.csv"))
```

# Create species list from IUCN data
```{r}
frugivore_species <- unique(frugivore_habitats$scientificName)
```

# Match species names to GBIF
```{r}
gbif_taxon_keys <- frugivore_species %>% 
name_backbone_checklist() %>% # match to backbone 
filter(!matchType == "NONE") %>% # get matched names
pull(usageKey) 
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
```
